UGAN: Improving Underwater Image Quality using Generative Adversarial Networks

### 2017-09-16 files/paper/tex/experiments.tex
update

\subsection{Comparison to CycleGAN}
It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance. We use the Canny edge
detector \cite{canny1986computational} to provide a color agnostic evaluation of the images, as the original contain
distorted colors and cannot be compared back to as ground truth. Due to the fact that restoring color information
should not alter the overall structure of the image, we measure the distance in the image space between the edges
found in the original and generated images. Figure ~\ref{fig:canny_samples} shows the original images and results from
edge detection. Table 1 provides the measurements from Figure ~\ref{fig:canny_samples}, as well as the average over the
entire dataset.

We explore the artifacts of content loss, as seen in Figure ~\ref{fig:zoom}. In particular, we compare local statistics
of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL
\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure. Laplacian stuff \cite{pertuz2013analysis}

@@

\begin{table}[ht]
\footnotesize
\centering
\caption{Gradient Difference Loss Metrics}
\begin{tabular}{| c | c | c | c | }
   \hline
   Patch/Method & CycleGAN & UGAN & UGAN-P \\ \hline
   Red    & 11.53 & 9.39 & 10.93  \\ \hline
   Blue   & 7.52  & 4.83 &  5.50\\ \hline
   Green  & 4.15  & 3.18 & 3.25 \\ \hline
   Orange & 6.72  & 5.65 & 5.79 \\ \hline
\end{tabular}
\end{table}

>>>>

\subsection{Comparison to CycleGAN}
It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
mapping $G: Y \rightarrow X$. Here we give a comparison to our methods. We use the Canny edge
detector \cite{canny1986computational} to provide a color agnostic evaluation of the images, as the original contain
distorted colors and cannot be compared back to as ground truth. Due to the fact that restoring color information
should not alter the overall structure of the image, we measure the distance in the image space between the edges
found in the original and generated images. Figure ~\ref{fig:canny_samples} shows the original images and results from
edge detection. Table 1 provides the measurements from Figure ~\ref{fig:canny_samples}, as well as the average over our
entire Flickr\texttrademark ~dataset. Both UGAN and UGAN-P are consistently closer in the image space to the original
than that of CycleGAN, suggesting noise due to blur. Next, we evaluate this noise explicitly.

We explore the artifacts of content loss, as seen in Figure ~\ref{fig:zoom}. In particular, we compare local statistics
of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL
\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure. A lower GDL measure implies a smoother transition
between pixels, as a noisy image would have large jumps in the image's gradient, leading to a higher score. \starnote{I THINK. I would double check, bottom of page 4: https://arxiv.org/pdf/1511.05440.pdf}.
As seen in Table \ref{fig:gdl_tbl}, the GDL is lower for both UGAN and UGAN-P. Interestingly, UGAN consistently has a
lower score than UGAN-P, despite UGAN-P explicitly accounting for this metric in the objective function. Reasoning for
this is left for our future work.

@@

\begin{table}[ht]
\footnotesize
\centering
\caption{Gradient Difference Loss Metrics}
\begin{tabular}{| c | c | c | c | }
   \hline
   Patch/Method & CycleGAN & UGAN & UGAN-P \\ \hline
   Red    & 11.53 & 9.39 & 10.93  \\ \hline
   Blue   & 7.52  & 4.83 &  5.50\\ \hline
   Green  & 4.15  & 3.18 & 3.25 \\ \hline
   Orange & 6.72  & 5.65 & 5.79 \\ \hline
\end{tabular}
\label{fig:gdl_tbl}
\end{table}
